Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-05 WSSSPE2_report/WSSSPE2_review.tex
My attempt to strengthen the abstract.

\begin{abstract}
This technical report records and discusses the Second Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE2). The workshop used an
alternative submission and peer-review process, which led to a set of papers
divided across five topic areas: exploring sustainability; software development
experiences; credit \& incentives; reproducibility \& reuse \& sharing; and code
testing \& code review. The report includes a description of the submission and
review process, the workshop keynote presentations, a series of lightning talks,
a discussion on sustainability, and the five discussions from the topic areas.
The report also contains a description of potential actions that were proposed
in the five discussions.
\end{abstract}

>>>>

\begin{abstract}
This technical report records and discusses the Second Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE2). 
%The workshop used an
%alternative submission and peer-review process, which led to a set of papers
%divided across five topic areas: 
The report includes a description of the alternative, experimental submission
and review process, two workshop keynote presentations, a series of lightning
talks, a discussion on sustainability, and five discussions from the topic areas
of exploring sustainability; software development experiences; credit \&
incentives; reproducibility \& reuse \& sharing; and code testing \& code
review. For each topic, the report includes a list of tangible actions that were
proposed and would lead to potential changes.

First and foremost, the workshop recognized that reliance on scientific software
is pervasive in all areas of world-leading research today. Then the workshop
participants proceeded to explore different perspectives on the concept of
sustainability. Key enablers and barriers of sustainable scientific software
were identified from the experiences of the workshop participants. In addition,
recommendations with new requirements such as software credit files and software
prize frameworks were outlined for improving practices in sustainable software
engineering.

There was also broad consensus that, within the disciplines represented, formal
training in software development or engineering was rare among the
practitioners. Significant strides are needed to be made in building a sense of
community via training in software and technical practices, on increasing their
size and scope, and on better integrating them directly into graduate education
programs.

Journals can define and publish policies to improve reproducibility, whereas
reviewers can insist that authors provide sufficient information and access to
data and software to allow them reproduce the results in the paper. Hence a list of
critieria is compiled for  journals to provide to reviewers so as to make it easier to
review software submitted for publication as a ``Software Paper.''

\end{abstract}
